---
title: "p8105_hw5"
author: "Ruilian Zhang"
date: "11/12/2021"
output: github_document
---

```{r}
library(tidyverse)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```


## Problem 1

```{r import and summary data}
homicide_df = 
  read_csv("data/homicide-data.csv", na = c(" ", "Unknown")) %>%
  janitor::clean_names() %>% 
  mutate(city_state = str_c(city, state, sep = ", ")) %>% 
  relocate(city_state) %>% 
  filter(city_state != "Tulsa, AL")

n_homicides_df = homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    n_homicides = n()
  )

n_unsolved_df = homicide_df %>% 
  group_by(city_state) %>% 
  filter(disposition %in% c("Closed without arrest", "Open/No arrest")) %>% 
  summarize(
    n_unsolved = n()
  )

city_summary_df = left_join(n_homicides_df, n_unsolved_df, by = "city_state") %>% 
  mutate(n_unsolved = replace_na(n_unsolved, 0))
```

```{r prop test baltimore}
baltimore_summary_df = 
  city_summary_df %>% 
  filter(city_state == "Baltimore, MD")

baltimore_prop = 
  prop.test(
    x = pull(baltimore_summary_df, n_unsolved), 
    n = pull(baltimore_summary_df, n_homicides), alternative = "two.sided")

baltimore_prop_tidy = broom::tidy(baltimore_prop, conf.int = TRUE)

pull(baltimore_prop_tidy, estimate)
c(pull(baltimore_prop_tidy, conf.low), pull(baltimore_prop_tidy, conf.high))
```

* For unsolved homicides in Baltimore, the estimated proportion is `r pull(baltimore_prop_tidy, estimate)`. The confidence interval is (`r c(pull(baltimore_prop_tidy, conf.low), pull(baltimore_prop_tidy, conf.high))`).

```{r proptest each city}
city_summary_nested = nest(city_summary_df, data = c("n_homicides", "n_unsolved"))

city_prop = function(df) {
  
  n = df[[1]]
  x = df[[2]]
  
  prop_test = prop.test(x = x, n = n, alternative = "two.sided") %>% 
    broom::tidy(conf.int = TRUE)
  
  tibble(
    est_unsolved_prop = round(pull(prop_test, estimate), 3),
    conf_int_lower = round(pull(prop_test, conf.low), 3),
    conf_int_upper = round(pull(prop_test, conf.high), 3)
    )
    
  }

city_prop_df = city_summary_nested %>% 
  mutate(prop_results = map(data, city_prop)) %>% 
  unnest(prop_results) %>% 
  select(-data)
```

```{r plot esitimaes and CIs}
city_prop_df %>% 
  ggplot(aes(x = reorder(city_state, est_unsolved_prop), y = est_unsolved_prop)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf_int_lower, ymax = conf_int_upper)) + 
  labs(
    title = "Estimated proportion of unsolved homicide for each city",
    y = "Estimated proportion",
    x = "City",
    caption = "Error bar shows 95% confidence interval"
  ) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

* The plot shows the estimated proportion of unsolved homicide for each city, in which the cities are ordered by estimated proportions.  
* Error bars show the confidence intervals for each proportion, which vary among cities. Cities such as `Tumpa FL` and `Svannah, GA` have wider confident intervals, while `Chicago, IL` has the narrowest one.
* `Richmond, VA` has the lowest estimated proportion, while `Chicago, IL` has the highest estimated proportion. 


## Problem 2

```{r read patient files and tidy, message = FALSE}
files = list.files(path = "data/problem_2")

read_files = function(x) {
  
  path = str_c("data/problem_2/", x)
  read_csv(path)
  
}

patient_df = 
  tibble(file_name = files) %>% 
  mutate(content = map(file_name, read_files)) %>% 
  unnest(content) %>% 
  separate(col = file_name, into = c("arm", "subject_id"), sep = "_") %>% 
  mutate(
    arm = ifelse(arm == "con", "control", "experimental"),
    subject_id = substr(subject_id, start = 1, stop = 2)) %>% 
  select(subject_id, everything()) %>% 
  pivot_longer(
    week_1:week_8, 
    names_to = "week",
    names_prefix = "week_",
    values_to = "value")

```

```{r make a plot}
patient_df %>% 
  ggplot(aes(x = week, y = value)) +
  geom_line(aes(group = subject_id, color = subject_id)) +
  facet_grid(. ~ arm) +
  labs(
    title = "Obsevered value over time for each patient",
    x = "Week",
    y = "Value"
  )
```

* Compared to the control group, all the patients in the experimental group has an increasing trend of detected value over time, with an approximate range of (-1, 7.5).    
* The values of the control group are relatively steady, which mostly fall within an interval of (-1.25, 3.75).  
* Patient 5 has the lowest overall values in control arm, but his/her values are relatively high among other patients in the experimental arm. And the situation is nearly the opposite for patient 3.  
* From the plot we may draw a conclusion that the experiment has a positive effect on increasing the test value.


## Problem 3

```{r introduce missing values}
set.seed(10)

iris_with_missing = iris %>% 
  map_df(~replace(.x, sample(1:150, 20), NA)) %>%
  mutate(Species = as.character(Species))
```



### need to be fixed
```{r write a funciton to fill NA}
fill_numeric = function(x) {
  
  mean = mean(x)
  
  for (i in 1:150) {
  
    is.na(x[i])
    if (TRUE) {
      x[i] = mean
    }
  }
}

fill_numeric(iris_with_missing$Sepal.Length)

iris_with_missing = map(.x = iris_with_missing$Sepal.Length, ~ fill_numeric(.x))
```

